DeepSphere: a graph-based spherical CNN

### 2019-09-23 main.tex
Updates from Overleaf
add climate figure

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{figure}[h]
	\includegraphics[height=0.25\linewidth]{example_cosmo_cmb}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_brain_meg}
% 	\hfill
% 	\includegraphics[height=0.25\linewidth]{example_climate_TMQ}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_ghcn_daily_tmax}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_ghcn_graph}
	\caption{
		Examples of intrinsically spherical data:
		(left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
		(middle) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
		(right) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, and the position of weather stations is arbitrary and changes over time.
		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
		%\todo{something from climate, weather?}
		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
		%\todo{horizontal colorbar for brain}
	}
	\label{fig:examples}
\end{figure}
\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}

@@

% 0.2 Explain why the Laplacian is so important...
By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian, i.e: $h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$\nati{Put this equation somewhere else?}.  Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if
% 0.3 Formulate the problem
\mart{Correct formula for equivariance error and the corresponding plots as soon as you changed it!}
\begin{equation} \label{eq:equivariance}
	\b{R}_V(g) \b{L} \b{f} = \b{L} \b{R}_V(g) \b{f} \hspace{1cm} \forall f\in F_V \text{ and } \forall g\in SO(3),
\end{equation}
where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{f}}}\right)^2,
\end{equation}
More generally for a class of signal $f \in C \subset F_V$, the \textit{mean equivariance error}
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g).
\end{equation}
\mart{Talk about the probability measure used on C, SO(3)?}
In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
The expected value is obtained by averaging over a finite number of random functions and random rotations.

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{figure}[h]
	\centering
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_cosmo_cmb}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
	} \hspace{0.1em}
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_climate_TMQ}
		\label{fig:examples:climate}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_daily_tmax}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_graph}
	}
	\caption{
		Examples of intrinsically spherical data:
		(a) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
		(c) hourly precipitation from a climate simulation \citep{mudigonda2017climateevents},
		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
		%\todo{something from climate, weather?}
		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
		%\todo{horizontal colorbar for brain}
	}
	\label{fig:examples}
\end{figure}
\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}

@@

% 0.2 Explain why the Laplacian is so important...
By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian, i.e: $h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$\nati{Put this equation somewhere else?}.  Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if
% 0.3 Formulate the problem
\mart{Correct formula for equivariance error and the corresponding plots as soon as you changed it!}
\begin{equation} \label{eq:equivariance}
	\b{R}_V(g) \b{L} \b{f} = \b{L} \b{R}_V(g) \b{f} \hspace{1cm} \forall f\in F_V \text{ and } \forall g\in SO(3),
\end{equation}
where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
\end{equation}
More generally for a class of signal $f \in C \subset F_V$, the \textit{mean equivariance error}
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g).
\end{equation}
\mart{Talk about the probability measure used on C, SO(3)?}
In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
The expected value is obtained by averaging over a finite number of random functions and random rotations.
